### 2022-10-31 CV2/general.tex
-

\section{Positions}
\begin{tabular}{rl}	
	\textsc{2022-Now}& Postdoctoral Researcher\\
	& \textbf{\href{https://uclouvain.be/en/index.html}{\color{black}Université catholique de Louvain}}, Louvain-la-Neuve, Belgium\\
\end{tabular}

@@

\section{Research Interests}
%Optimization Algorithms, Distributed Optimization, Machine Learning
\begin{tabular}{cl}
	\qquad\qquad&  Optimization\\
	& Federated and Distributed Learning\\
	&  Machine Learning
\end{tabular}

@@

\begin{tabular}{rl}
	\textsc{Programming} & C/C++, Python, Algorithms and Data Structures\\& \textsc{Past experience:} Go, C\#, VB.NET, SQL, Julia\\
	\textsc{Mathematics} & Calculus, Linear Algebra, Probability and Statistics, Convex Analysis\\
	\textsc{Computer} & macOS, LaTeX, Git\\
\end{tabular}

>>>>

\section{Positions}
\begin{tabular}{rl}	
	\textsc{2022-Now}& Postdoctoral Researcher\\
	& \textbf{\href{https://uclouvain.be/en/index.html}{\color{black}Université catholique de Louvain}}, Louvain-la-Neuve, Belgium\\
	\textsc{2022}& Researcher\\
	&Laboratory of Advanced Combinatorics and Network Applications\\
	&\textbf{\href{https://mipt.ru/}{\color{black}Moscow Institute of Physics and Technology}}, Dolgoprudny, Russia\\
	\textsc{2021-2022}& Research Intern\\
	 &Research Center for Trusted Artificial Intelligence\\
	 &\textbf{\href{https://www.ispras.ru/en/}{\color{black}Ivannikov Institute for System Programming}}, Moscow, Russia
\end{tabular}

@@

\section{Research Interests}
%Optimization Algorithms, Distributed Optimization, Machine Learning
\begin{tabular}{cl}
	&  Optimization\\
	& Federated and Distributed Learning\\
	&  Machine Learning
\end{tabular}

@@

\begin{tabular}{rl}
	\textsc{Programming} & C/C++, Python, Algorithms and Data Structures, Jax, Pytorch\\
	& \textsc{Past experience:} Go, C\#, VB.NET, SQL, Julia, HTML/CSS\\
	\textsc{Mathematics} & Calculus, Linear Algebra, Probability and Statistics, Convex Analysis\\
	\textsc{Computer} & macOS, LaTeX, Git\\
\end{tabular}

### 2022-10-31 CV2/teaching.tex
-

\begin{enumerate}
	\item \teaching{Mentor for 2 Research Projects with Students: Grigory Malinovsky and Abdurakhmon Sadiev}{King Abdullah University of Science and Technology, Thuwal, Saudi Arabia}{March 2022}

%	Mini-seminar for

@@

	\item \teaching{Mentor for a Research Project with Student Grigory Malinovsky (resulted in ICML 2020 paper <<From Local SGD to Local Fixed Point Methods for Federated Learning>>)}{King Abdullah University of Science and Technology, Thuwal, Saudi Arabia}{January 2020}

%	 {\bf Project Mentor at <<Modern Information, Optimization and Control Methods>> Educational Program}, Sirius University, Sochi, Russia (July-August 2021)

>>>>

\begin{enumerate}

	\item \teaching{Mentor for a Research Project with MIPT student Ekaterina Borodich (online, led to NeurIPS 2022 paper <<Optimal Gradient Sliding and its Application to Distributed Optimization Under Similarity>>)}{Moscow Institute of Physics and Technology, Moscow, Russia}{March 2022}

	\item \teaching{Mentor for a Research Project with KAUST Student Abdurakhmon Sadiev (led to NeurIPS 2022 paper <<Communication Acceleration of Local Gradient Methods via an Accelerated Primal-Dual Algorithm with Inexact Prox>>)}{King Abdullah University of Science and Technology, Thuwal, Saudi Arabia}{March 2022}

@@

	\item \teaching{Mentor for a Research Project with Student Grigory Malinovsky (done during his internship at KAUST, led to ICML 2020 paper <<From Local SGD to Local Fixed Point Methods for Federated Learning>>)}{King Abdullah University of Science and Technology, Thuwal, Saudi Arabia}{January 2020}
